Title Goes Here

### 2019-04-18 analysis/paper/paper.Rmd
update manuscript

---
title             : "Overt attentional capture by reward-related stimuli overcomes top-down suppression"
shorttitle        : "Reward overcomes attentional suppression"

@@

Recently, a hybrid model of attentional selection has been proposed---the *signal suppression hypothesis* [@Gaspelin2018; @Sawaki2010]---which attempts to integrate these two competing accounts. According to this model, salient stimuli automatically generate an attentional priority signal (or "attend-to-me" signal) that will go on to capture attention unless it is suppressed by a top-down control process, which builds over repeated experience with the salient stimulus [@Gaspelin2018b]. This account is consistent with stimulus-driven theories, in that it proposes that physically salient stimuli have the potential to involuntarily capture attention; however it is also consistent with goal-directed theories in that it proposes that there is some top-down control of the allocation of attention. Evidence supporting the signal suppression hypothesis has largely come from the event-related potential (ERP) literature [for review, see @Gaspelin2018a], however recent studies have demonstrated behavioural evidence of suppression in the context of overt attention [i.e., eye-movements: see @Gaspelin2016; @Gaspelin2018b; @Ipata2006] and covert attention [i.e., shifts of attention that are not accompanied by eye-movements: see @Gaspelin2015].

For example, across two experiments @Gaspelin2016 had participants perform variants of a commonly used  procedure for examining attentional capture---the *additional singleton task* [@Theeuwes1991a; @Theeuwes1992]---while recording eye movements. Eye movements provide a useful index of attention since an eye movement to a location (a saccade) is necessarily preceded by a shift of spatial attention to that location [@Deubel1996]. In this task, participants were required to locate and respond to a shape-singleton target that was presented in an array of non-target shapes. On half of the trials, one of the non-target shapes was rendered in a different colour from the rest of the array so as to be a physically salient colour-singleton distractor. If participants were *more* likely to make a saccade towards the singleton distractor than one of the nonsingleton non-targets, this would indicate that the singleton distractor had captured attention. By contrast, if participants were *less* likely to make a saccade to the singleton distractor than one of the nonsingleton non-targets, this would suggest that attention to the singleton distractor had been suppressed. In @Gaspelin2016\'s Experiment 1, participants were encouraged to adopt a strategy of searching for the "odd-one-out" in the display [i.e, *singleton-search mode*; @Bacon1994], by having the target be randomly either a circle amongst diamonds or a diamond amongst circles on each trial (see Figure \@ref(fig:methodFig)A for an example from the current study). Under these conditions, both stimulus-driven [@Theeuwes1992] and goal-directed [@Bacon1994] accounts of attentional selection would predict capture, as the template that participants use to locate the target (i.e., any singleton) is broad enough to include the singleton distractor. As expected, under these singleton-search conditions Gaspelin et al. found that participants' overt attention was captured by the salient singleton. In Experiment 2, participants were instead encouraged to adopt a more specific target template [i.e., *feature-search mode*; @Bacon1994], by consistently mapping the target identity to one shape (e.g., search for a circle on every trial), and having a heterogeneous set of shapes act as the non-targets (see Figure \@ref(fig:methodFig)B). This manipulation makes searching for any singleton a highly inefficient strategy, as there are multiple singleton nontargets in the display (e.g., a circle, a square, a triangle, and a red shape). Thus, participants should be encouraged to search for the specific features that define the target (i.e., the "circleness" of the circle). Under these conditions, attention to the salient colour-singleton distractor was suppressed relative to the other non-targets, suggesting that it was treated differently from the other non-targets (inconsistent with goal-directed accounts), yet did not capture gaze (inconsistent with stimulus-driven accounts). By contrast, the signal suppression hypothesis can account for these findings by suggesting that the singleton generated an attentional priority signal as a consequence of its physical salience, but this signal could be suppressed by top-down control under conditions that promote a more specific search strategy (i.e., feature search). Importantly, this suppression effect was observed even for the most rapidly generated eye movements, which was taken as evidence that the suppression effect operates early in processing, before attention is initially allocated.

@@

Pairing a stimulus with reward is thought to increase its attentional priority in a way that mimics or otherwise interacts with its physical salience. For example, eye-tracking studies have demonstrated that VMAC is largest for the most rapidly generated saccades, and diminishes with increasing saccade latency [@Pearson2016; @Failing2015], a pattern similar to that observed in capture by physical salience [e.g., @VanZoest2004]. Similarly, electrophysiological studies have shown that reward affects ERP components thought to index low-level perceptual activity [@Hickey2010]. This is consistent with the idea of *incentive salience* [@Berridge1998], wherein a reward-related stimulus becomes more salient and attention grabbing to the observer through a change in its perceptual representation. This begs the question, if associating a stimulus with reward increases its perceptual priority as though it has become more physically salient, can this priority signal be suppressed by the top-down control process proposed by the signal suppression hypothesis? That is, can incentive salience be suppressed in the same way as physical salience? Aside from the theoretical importance of this question, it may also have important clinical implications. Recent evidence suggests that the processes underlying VMAC are closely related to the attentional biases towards drug-related stimuli observed in addiction [@Albertella2017a; @Anderson2013; for review see @Field2008], which can promote relapse in recovering addicts [@Marissen2006; @Waters2012; @Marhe2013]. Thus it is important to know whether top-down cognitive control processes can be used to overcome the influence of reward on attention when such capture is counterproductive and contrary to our goals. We addressed this question by combining Le Pelley et al.'s VMAC procedure with Gaspelin et al.'s (2017) overt attentional suppression procedure to investigate whether reward-related attentional biases can be suppressed by top-down control processes under conditions promoting feature search.

@@

## Stimuli
The task was based on that used by @Gaspelin2016 and Pearson et al. [-@Pearson2015; -@Pearson2016]. Each trial consisted of a fixation display, a search display, and a feedback display (see Figure \@ref(fig:methodFig)C). All stimuli were presented on a black background. The fixation display consisted of a white cross (0.5$^\circ$ visual angle), presented in the centre of the screen and surrounded by a white circle (diameter 3.0$^\circ$). The search display consisted of four filled shapes (size 1.6$^\circ$ $\times$ 1.6$^\circ$) presented above, below, left and right of screen centre (eccentricity 4.5$^\circ$). One of the shapes was designated as the target, and the other three shapes were designated non-targets. For all participants, the target was randomly determined to be either a circle or a diamond on each trial [^1]. The identity of the non-target shapes varied by search condition. For the *singleton search* condition, the non-target stimuli were all rendered as the alternative target shape (i.e., if the target was a diamond, all of the non-targets were circles; Figure \@ref(fig:methodFig)B). For the *feature search* condition, the non-target stimuli were randomly selected without replacement from a set of two squares and two hexagons, and were never rendered as the alternative target shape (Figure \@ref(fig:methodFig)C). The target and two of the non-targets were always rendered in grey (CIE $x$,$y$ chromaticity coordinates of .327/.400). On the majority of trials, one of the non-target shapes (the *singleton distractor*) was rendered in either orange or blue (CIE $x$,$y$ coordinates .492/.445 and .192/.216, respectively). On the remaining trials, all shapes were rendered in grey such that there was no singleton distractor. The values of blue and orange had similar luminance (~24.5 cd/m^2^), which was higher than that of grey (~8.3 cd/m^2^). The feedback display showed the points earned on the current trial. If the response time (RT) exceeded the soft-timeout threshold (see below), the message "Too slow" appeared below the reward feedback.

@@

[^2]: Note that the comparison of interest in determining whether a stimulus captured attention, or was otherwise suppressed, is the percentage of first saccades to the singleton vs. the average nonsingleton distractor. Thus, while we have included the percentage of first saccades to the target in Figure \@ref(fig:SaccadePlot) for the sake of completeness, we have not included these data in our analyses.

Next we tested whether overt attention to each distractor type was captured or suppressed in each search condition. Planned one-sample *t*-tests showed that capture scores were significantly greater than zero (indicating that overt attention was captured by the high-reward singleton) under conditions promoting singleton search, `r apa_print(Singleton_high.ttest)$statistic`, $d_z=$ `r Singleton_high.es`, as well as feature search, `r apa_print(Feature_high.ttest)$statistic`, $d_z=$ `r Feature_high.es`. For the low-reward distractor, there was a non-significant numerical trend towards capture in the singleton search condition, `r apa_print(Singleton_low.ttest)$statistic`, $d_z=$ `r Singleton_low.es`. In contrast, for the feature search condition, capture score was significantly below zero, `r apa_print(Feature_low.ttest)$statistic`, $d_z=$ `r Feature_low.es`, indicating that overt attention to the low-reward singleton was suppressed. Thus, in line with previous findings [@Gaspelin2016], our data suggest that overt attention to physically salient singletons can be suppressed when participants are encouraged to adopt a specific target template. However, singletons that have been associated with high-reward reward capture overt attention, regardless of participants' target template and despite such capture being directly counterproductive to earning reward.

@@

## Attentional capture/suppression effects for the fastest quartile of saccadic latencies
To investigate the time course of the overt attentional capture and suppression effects, we analysed capture scores (proportion of first saccades towards the singleton distractor minus the average nonsingleton distractor) on high-reward and low-reward trials as a function of saccade latency using the Vincentizing procedure [@Ratcliff1979]. We calculated mean saccade latency and capture score separately for each trial type and quartile of the individual saccade latency distributions. We then analysed the capture scores for the most rapidly generated saccades. According to the signal suppression hypothesis, the top-down suppression effect is activated early in processing, prior to the initial allocation of attention [@Gaspelin2018a]. Therefore the speed with which a saccade is initiated should have no effect on the extent to which overt attention can be suppressed. As illustrated in Figure \@ref(fig:VincentizedPlot), the most rapidly generated saccades were captured by the high-reward singleton (capture scores $>0$) in both the singleton search, `r apa_print(vincentized_singleton_high_q1.ttest)$statistic`, $d_z=$ `r vincentized_singleton_high_q1.es`, and feature search conditions, `r apa_print(vincentized_feature_high_q1.ttest)$statistic`, $d_z=$ `r vincentized_feature_high_q1.es`. Similarly, the the most rapidly generated saccades were captured by the low-reward singleton in both the singleton search, `r apa_print(vincentized_singleton_low_q1.ttest)$statistic`, $d_z=$ `r vincentized_singleton_low_q1.es`, and feature search conditions, `r apa_print(vincentized_feature_low_q1.ttest)$statistic`, $d_z=$ `r vincentized_feature_low_q1.es`. It is notable that we observed capture (rather than suppression) for the fastest saccades for both trial-types in the feature search condition. This finding is inconsistent with Gaspelin et al.’s [-@Gaspelin2016] previous report of attentional suppression of physically salient singleton distractors in the fastest eye-movements.

# Discussion
In this experiment, we investigated the role of top-down control processes in actively suppressing overt attention to physically salient and reward-associated distractor stimuli. In line with the signal suppression hypothesis [@Gaspelin2016; @Gaspelin2015], we found that overt attention to physically salient colour singleton distractors can be actively suppressed under conditions that promote top-down guidance of attention. Consistent with recent findings [@Gaspelin2018b; @Vatterott2012], this attentional suppression effect gradually emerged over the course of the experiment, as participants gained experience with the physically salient distractor feature. Furthermore, we found an effect of reward association on overt attention [i.e., VMAC; @LePelley2015b; @Pearson2015], with participants' gaze more likely to be captured by distractor stimuli that signalled high reward than low reward, even though looking at reward-signalling distractors caused omission of rewards that otherwise would have been delivered. Similar to the attentional suppression effect, attentional capture by reward-associated distractors also emerged over the course of the experiment, as participants experienced more pairings of stimulus features with reward. Critically, this study was the first to demonstrate that---unlike the influence of physical salience---the influence of reward association on attention cannot be suppressed under conditions that promote top-down guidance of attention. Regardless of whether participants were encouraged to search for specific target defining features (i.e., feature search mode) or to search for the odd-one-out (singleton search mode), stimuli associated with high reward captured overt attention. Notably, this attentional bias was counterproductive, in that it led to the omission of more high rewards than low rewards, and so participants should have been highly motivated to suppress their attention to the high-reward distractor if possible. Nevertheless, the high-reward distractor captured attention, even under conditions that allowed participants to suppress their attention to physically salient distractors that were associated with low reward. Our key finding, then, is that reward-related stimuli constitute especially potent attentional priority signals that are relatively immune to suppression by top-down control processes that can act to prevent distraction by physical salience.

Most influential models of attentional selection assume that stimulus-driven and goal-directed influences are integrated onto a common priority map in the brain, with attention directed towards the spatial location with the highest peak of activation [e.g., @Itti2001; @Theeuwes2010; @Wolfe2007]. The priority map concept has also been used to explain how selection history influences attentional allocation [@Awh2012; @Failing2018], with the attentional priority signal of reward-related stimulus features increasing with repeated stimulus-reward pairings through a process of associative learning [@Pearson2016; @LePelleya]. Recent formulations of the signal suppression hypothesis have suggested that the top-down suppression mechanism may operate in a similar way, with the attentional priority of to-be-ignored stimulus features being proactively downweighted with repeated experience [@Gaspelin2018a]. At first glance, the results of the current study may seem inconsistent with the idea that reward and top-down suppression engage in competition on a common priority map, as the magnitude of the VMAC effect did not differ between search conditions, even though the feature search condition should have encouraged top-down guidance of attention. However, there was an overall decrease in the amount of capture by both the high- and low-reward distractor in the feature search condition This raises the possibility that repeated experience of the physically salient stimulus features (i.e., orange and blue colour) allows the attentional priority of those features to be uniformly downweighted by the top-down suppression mechanism. In addition, our findings are consistent with the idea that repeated experience of the stimulus feature-reward pairings selectively upweights the attentional priority of the high-reward distractor, such that it overpowers the influence of top-down suppression and thus captures attention.

An inconsistency between the results of the current study and that of @Gaspelin2016 comes from the time-course of the attentional capture and suppression effects that were observed. According to the signal suppression hypothesis, top-down suppression operates prior to the initial allocation of attention, and so suppression should be observed even for the most rapidly generated saccades. Consistent with this idea, @Gaspelin2016 observed an overt attentional suppression effect to physically salient singleton distractors amongst the fastest quartile of saccade latencies. In contrast, in the current experiment we observed overt attentional capture in the fastest quartile of saccade latencies, with the suppression effect emerging on trials with slower saccades. Methodological differences between Gaspelin et al.'s  [-@Gaspelin2016] experiment and the current study may be responsible for this discrepancy. For example, the availability of reward on low-reward trials may have influenced capture, either by somewhat increasing the attentional priority of the stimulus feature associated with low-reward reward, or by otherwise influencing participants' motivation to respond quickly. Alternatively, the discrepancy in findings may reflect our use of two potential targets (circle and diamond) in the feature search condition, as opposed to the same target on all trials in Gaseplin et al.'s procedure. Having two possible targets could reduce the influence of trial-by-trial upweighting of target features [@Maljkovic1994], but may also result in less effective feature search [e.g., @Houtkamp2009; but see @Grubert2015]. How these methodological differences might influence the time-course of overt attentional capture and suppression remains a question for future research. Nonetheless, the finding does raise questions about whether the attentional suppression effect that we have observed is truly the result of proactive top-down suppression of salient stimuli, as suggested by the signal suppression hypothesis, or potentially the result of rapid covert disengagement from the salient stimuli [see @Theeuwes2010; @VanZoest2004 for similar arguments].

As mentioned previously, attentional capture by stimuli associated with monetary rewards can be mapped on to the attentional biases to drug-related stimuli seen in addiction. Indeed, recent findings suggest that these biases may be the result of a common mechanism [@Anderson2013; @Albertella2017a]. This is consistent with the idea of incentive salience [@Berridge1998], where the perceptual representation of an otherwise neutral stimulus is modified so as to become more salient and attention grabbing to the observer, as a result of its association with a desired outcome (e.g., drugs, money). The current study suggests that incentive salience has a particularly powerful influence on the attentional system, overcoming top-down control mechanisms that can effectively prevent capture by physically salient stimuli. This may have implications for the development of treatments for substance use disorders that target these attentional biases.

>>>>

---
title             : "Overt attentional capture by reward-related stimuli overcomes inhibitory suppression"
shorttitle        : "Reward overcomes attentional suppression"

@@

Recently, a hybrid model of attentional selection has been proposed---the *signal suppression hypothesis* [@Gaspelin2018; @Sawaki2010]---which attempts to integrate these two competing accounts. According to this model, salient stimuli automatically generate an attentional priority signal (or "attend-to-me" signal) that will go on to capture attention unless it is suppressed by an inhibitory control process, which builds over repeated experience with the salient stimulus [@Gaspelin2018b]. This account is consistent with stimulus-driven theories, in that it proposes that physically salient stimuli have the potential to involuntarily capture attention; however it is also consistent with goal-directed theories in that it proposes that there is some top-down control of the allocation of attention. Evidence supporting the signal suppression hypothesis has largely come from the event-related potential (ERP) literature [for review, see @Gaspelin2018a], however recent studies have demonstrated behavioural evidence of suppression in the context of overt attention [i.e., eye-movements: see @Gaspelin2016; @Gaspelin2018b; @Ipata2006] and covert attention [i.e., shifts of attention that are not accompanied by eye-movements: see @Gaspelin2015].

For example, across two experiments @Gaspelin2016 had participants perform variants of a commonly used  procedure for examining attentional capture---the *additional singleton task* [@Theeuwes1991a; @Theeuwes1992]---while recording eye movements. Eye movements provide a useful index of attention since an eye movement to a location (a saccade) is necessarily preceded by a shift of spatial attention to that location [@Deubel1996]. In this task, participants were required to locate and respond to a shape-singleton target that was presented in an array of non-target shapes. On half of the trials, one of the non-target shapes was rendered in a different colour from the rest of the array so as to be a physically salient colour-singleton distractor. If participants were *more* likely to make a saccade towards the singleton distractor than one of the nonsingleton non-targets, this would indicate that the singleton distractor had captured attention. By contrast, if participants were *less* likely to make a saccade to the singleton distractor than one of the nonsingleton non-targets, this would suggest that attention to the singleton distractor had been suppressed. In @Gaspelin2016\'s Experiment 1, participants were encouraged to adopt a strategy of searching for the "odd-one-out" in the display [i.e, *singleton-search mode*; @Bacon1994], by having the target be randomly either a circle amongst diamonds or a diamond amongst circles on each trial (see Figure \@ref(fig:methodFig)A for an example from the current study). Under these conditions, both stimulus-driven [@Theeuwes1992] and goal-directed [@Bacon1994] accounts of attentional selection would predict capture, as the template that participants use to locate the target (i.e., any singleton) is broad enough to include the singleton distractor. As expected, under these singleton-search conditions Gaspelin et al. found that participants' overt attention was captured by the salient singleton. In Experiment 2, participants were instead encouraged to adopt a more specific target template [i.e., *feature-search mode*; @Bacon1994], by consistently mapping the target identity to one shape (e.g., search for a circle on every trial), and having a heterogeneous set of shapes act as the non-targets (see Figure \@ref(fig:methodFig)B). This manipulation makes searching for any singleton a highly inefficient strategy, as there are multiple singleton nontargets in the display (e.g., a circle, a square, a triangle, and a red shape). Thus, participants should be encouraged to search for the specific features that define the target (i.e., the "circleness" of the circle). Under these conditions, attention to the salient colour-singleton distractor was suppressed relative to the other non-targets, suggesting that the visual attention system treated the salient singleton differently from the other non-targets (inconsistent with goal-directed accounts), yet did not capture gaze (inconsistent with stimulus-driven accounts). By contrast, the signal suppression hypothesis can account for these findings by suggesting that the singleton generated an attentional priority signal as a consequence of its physical salience, but this signal could be suppressed by an inhibitory mechanism under conditions that promoted a more specific search strategy (i.e., feature search). Importantly, this suppression effect was observed even for the most rapidly generated eye movements, which was taken as evidence that the suppression effect operates early in processing, before attention is initially allocated.

@@

Pairing a stimulus with reward is thought to increase its attentional priority in a way that mimics or otherwise interacts with its physical salience. For example, eye-tracking studies have demonstrated that VMAC is largest for the most rapidly generated saccades, and diminishes with increasing saccade latency [@Pearson2016; @Failing2015], a pattern similar to that observed in capture by physical salience [e.g., @VanZoest2004]. Similarly, electrophysiological studies have shown that reward affects ERP components thought to index low-level perceptual activity [@Hickey2010]. This is consistent with the idea of *incentive salience* [@Berridge1998], wherein a reward-related stimulus becomes more salient and attention grabbing to the observer through a change in its perceptual representation. This raises the question, if associating a stimulus with reward increases its perceptual priority as though it has become more physically salient, can this priority signal be suppressed by the inhibitory control process proposed by the signal suppression hypothesis? That is, can incentive salience be suppressed in the same way as physical salience? Aside from the theoretical importance of this question, it may also have important clinical implications. Recent evidence suggests that the processes underlying VMAC are closely related to the attentional biases towards drug-related stimuli observed in addiction [@Albertella2017a; @Anderson2013; for review see @Field2008], which can promote relapse in recovering addicts [@Marissen2006; @Waters2012; @Marhe2013]. Thus it is important to know whether cognitive control processes can be used to overcome the influence of reward on attention when such capture is counterproductive and contrary to our goals. We addressed this question by combining Le Pelley et al.'s VMAC procedure with Gaspelin et al.'s (2017) overt attentional suppression procedure to investigate whether reward-related attentional biases can be suppressed by inhibitory control processes under conditions promoting feature search.

@@

## Stimuli
The task was based on that used by @Gaspelin2016 and Pearson et al. [-@Pearson2015; -@Pearson2016]. Each trial consisted of a fixation display, a search display, and a feedback display (see Figure \@ref(fig:methodFig)C). All stimuli were presented on a black background. The fixation display consisted of a white cross (0.5$^\circ$ visual angle), presented in the centre of the screen and surrounded by a white circle (diameter 3.0$^\circ$). The search display consisted of four filled shapes (size 1.6$^\circ$ $\times$ 1.6$^\circ$) presented above, below, left and right of screen centre (eccentricity 4.5$^\circ$). One of the shapes was designated as the target, and the other three shapes were designated non-targets. For all participants, the target was randomly determined to be either a circle or a diamond on each trial [^1]. The identity of the non-target shapes varied by search condition. For the *singleton search* condition, the non-target stimuli were all rendered as the alternative target shape (i.e., if the target was a diamond, all of the non-targets were circles; Figure \@ref(fig:methodFig)B). For the *feature search* condition, the non-target stimuli were randomly selected without replacement from a set of two squares and two hexagons (such that one of the non-targets was always a shape singleton), and were never rendered as the alternative target shape (Figure \@ref(fig:methodFig)C). The target and two of the non-targets were always rendered in grey (CIE $x$,$y$ chromaticity coordinates of .327/.400). On the majority of trials, one of the non-target shapes (the *singleton distractor*) was rendered in either orange or blue (CIE $x$,$y$ coordinates .492/.445 and .192/.216, respectively). On the remaining trials, all shapes were rendered in grey such that there was no singleton distractor. The values of blue and orange had similar luminance (~24.5 cd/m^2^), which was higher than that of grey (~8.3 cd/m^2^). The feedback display showed the points earned on the current trial. If the response time (RT) exceeded the soft-timeout threshold (see below), the message "Too slow" appeared below the reward feedback.

@@

[^2]: Note that the comparison of interest in determining whether a stimulus captured attention, or was suppressed, is the percentage of first saccades to the singleton vs. the average nonsingleton distractor. Thus, while we have included the percentage of first saccades to the target in Figure \@ref(fig:SaccadePlot) for the sake of completeness, we have not included these data in our analyses.

Next we tested whether overt attention to each distractor type was captured or suppressed in each search condition. Planned one-sample *t*-tests showed that capture scores were significantly greater than zero (indicating that overt attention was captured by the high-reward singleton) under conditions promoting singleton search, `r apa_print(Singleton_high.ttest)$statistic`, $d_z=$ `r Singleton_high.es`, as well as feature search, `r apa_print(Feature_high.ttest)$statistic`, $d_z=$ `r Feature_high.es`. For the low-reward distractor, there was a non-significant numerical trend towards capture in the singleton search condition, `r apa_print(Singleton_low.ttest)$statistic`, $d_z=$ `r Singleton_low.es`. In contrast, for the feature search condition, capture score was significantly below zero, `r apa_print(Feature_low.ttest)$statistic`, $d_z=$ `r Feature_low.es`, indicating that overt attention to the low-reward singleton was suppressed. Thus, in line with previous findings [@Gaspelin2016], our data suggest that overt attention to physically salient singletons can be suppressed when participants are encouraged to adopt a specific target template. However, singletons that have been associated with high reward capture overt attention, regardless of participants' target template and despite such capture being directly counterproductive to earning reward.

@@

## Attentional capture/suppression effects for the fastest quartile of saccadic latencies
To investigate the time course of the overt attentional capture and suppression effects, we analysed capture scores (proportion of first saccades towards the singleton distractor minus the average nonsingleton distractor) on high-reward and low-reward trials as a function of saccade latency using the Vincentizing procedure [@Ratcliff1979]. We calculated mean saccade latency and capture score separately for each trial type and quartile of the individual saccade latency distributions. We then analysed the capture scores for the data from the first quartile of this distribution, i.e., the most rapidly generated saccades. According to the signal suppression hypothesis, the attentional suppression effect is activated early in processing, prior to the initial allocation of attention [@Gaspelin2018a]. Therefore the speed with which a saccade is initiated should have no effect on the extent to which overt attention can be suppressed. As illustrated in Figure \@ref(fig:VincentizedPlot), the most rapidly generated saccades were captured by the high-reward singleton (capture scores $>0$) in both the singleton search, `r apa_print(vincentized_singleton_high_q1.ttest)$statistic`, $d_z=$ `r vincentized_singleton_high_q1.es`, and feature search conditions, `r apa_print(vincentized_feature_high_q1.ttest)$statistic`, $d_z=$ `r vincentized_feature_high_q1.es`. Similarly, the most rapidly generated saccades were captured by the low-reward singleton in both the singleton search, `r apa_print(vincentized_singleton_low_q1.ttest)$statistic`, $d_z=$ `r vincentized_singleton_low_q1.es`, and feature search conditions, `r apa_print(vincentized_feature_low_q1.ttest)$statistic`, $d_z=$ `r vincentized_feature_low_q1.es`. It is notable that we observed capture (rather than suppression) for the fastest saccades for both trial-types in the feature search condition. This finding is inconsistent with Gaspelin et al.’s [-@Gaspelin2016] previous report of attentional suppression of physically salient singleton distractors in the fastest eye-movements.

# Discussion
In this experiment, we investigated the role of inhibitory control processes in actively suppressing overt attention to physically salient and reward-associated distractor stimuli. In line with the signal suppression hypothesis [@Gaspelin2016; @Gaspelin2015], overt attention to physically salient colour singleton distractors was suppressed under conditions that promoted top-down guidance of attention. Specifically, under feature search conditions, participants were generally less likely to look at a (low-reward) colour singleton distractor than the average nonsingleton distractor. Consistent with recent findings [@Gaspelin2018b; @Vatterott2012], this attentional suppression effect gradually emerged over the course of the experiment, as participants gained experience with the salient-but-irrelevant distractor feature (Figure \@ref(fig:blockPlot)). Furthermore, we observed an effect of reward association on overt attention [i.e., VMAC; @LePelley2015b; @Pearson2015], with participants' gaze more likely to be captured by distractor stimuli that signalled high reward than low reward, even though looking at reward-signalling distractors caused omission of rewards that otherwise would have been delivered. Similar to the attentional suppression effect, attentional capture by reward-associated distractors also emerged over the course of the experiment, as participants experienced more pairings of stimulus features with reward. Critically, this study was the first to demonstrate that---unlike the influence of physical salience---the influence of reward association on attention cannot be suppressed under conditions that promote top-down guidance of attention. Regardless of whether participants were encouraged to search for specific target defining features (i.e., feature search mode) or to search for the odd-one-out (singleton search mode), stimuli associated with high reward captured overt attention. Notably, this attentional bias was counterproductive, in that it led to the omission of more high rewards than low rewards, and so participants should have been highly motivated to suppress their attention to the high-reward distractor if possible. Nevertheless, the high-reward distractor captured attention, even under conditions that allowed participants to suppress their attention to physically salient distractors that were associated with low reward. Our key finding, then, is that reward-related stimuli constitute especially potent attentional priority signals that are relatively immune to suppression by inhibitory control processes that can act to prevent distraction by physical salience.

Most influential models of attentional selection assume that stimulus-driven and goal-directed influences are integrated onto a common priority map in the brain, with attention directed towards the spatial location with the highest peak of activation [e.g., @Itti2001; @Theeuwes2010; @Wolfe2007]. The priority map concept has also been used to explain how selection history influences attentional allocation [@Awh2012; @Failing2018], with the attentional priority signal of reward-related stimulus features increasing with repeated stimulus-reward pairings through a process of associative learning [@Pearson2016; @LePelleya]. Recent formulations of the signal suppression hypothesis have suggested that the attentional suppression mechanism may operate in a similar way, with the attentional priority of to-be-ignored stimulus features being proactively down-weighted with repeated experience [@Gaspelin2018a]. At first glance, the results of the current study may seem inconsistent with the idea that reward and suppression engage in competition on a common priority map, as the magnitude of the VMAC effect did not differ between search conditions, even though the feature search condition should have encouraged top-down guidance of attention. However, there was an _overall_ decrease in the amount of capture by both the high- and low-reward distractor in the feature search condition (supported by a main effect of search condition, e.g., see Figures \@ref(fig:SaccadePlot)B and \@ref(fig:SaccadePlot)D). This raises the possibility that repeated experience of the physically salient stimulus features (i.e., orange and blue colour) allows the attentional priority of those features to be uniformly down-weighted by the suppression mechanism. In addition, our findings are consistent with the idea that repeated experience of pairings between stimulus features and reward results in selective up-weighting of the attentional priority of the high-reward distractor, such that it overpowers the influence of inhibitory suppression and thus captures attention.

An inconsistency between the results of the current study and those of @Gaspelin2016 comes from the time-course of the attentional capture and suppression effects that were observed. According to the signal suppression hypothesis, suppression is _proactive_---in that it operates prior to the initial allocation of attention---and so suppression should be observed even for the most rapidly generated saccades. Consistent with this idea, @Gaspelin2016 observed an overt attentional suppression effect to physically salient singleton distractors amongst the fastest quartile of saccade latencies. By contrast, in the current experiment we observed overt attentional capture in the fastest quartile of saccade latencies, with the suppression effect emerging on trials with slower saccades. Methodological differences between Gaspelin et al.'s  [-@Gaspelin2016] experiment and the current study may be responsible for this discrepancy. For example, the availability of reward on low-reward trials may have influenced capture, either by somewhat increasing the attentional priority of the stimulus feature associated with low reward, or by otherwise influencing participants' motivation to respond quickly. Alternatively, the discrepancy in findings may reflect our use of two potential targets (circle and diamond) in the feature search condition, as opposed to the same target on all trials in Gaseplin et al.'s procedure. Having two possible targets could reduce the influence of trial-by-trial upweighting of target features [@Maljkovic1994], but may also result in less effective feature search [e.g., @Houtkamp2009; but see @Grubert2015]. Another possible explanation comes from the use of an intermixed trial structure: as participants randomly experienced trials containing either the high- or low-reward colour throughout the course of the task, it is possible that the proactive down-weighting of the salient-but-irrelevant features could not build up enough to prevent capture for the most rapidly initiated saccades [@Gaspelin2018a]. How these methodological differences might influence the time-course of overt attentional capture and suppression remains a question for future research. Nonetheless, the finding does raise questions about whether the attentional suppression effect that we have observed is truly the result of proactive attentional suppression of salient stimuli, as suggested by the signal suppression hypothesis, or potentially the result of rapid covert disengagement from the salient stimuli [see @Theeuwes2010; @VanZoest2004 for similar arguments].

As mentioned previously, attentional capture by stimuli associated with monetary rewards can be mapped on to the attentional biases to drug-related stimuli seen in addiction. Indeed, recent findings suggest that these biases may be the result of a common mechanism [@Anderson2013; @Albertella2017a]. This is consistent with the idea of incentive salience [@Berridge1998], where the perceptual representation of an otherwise neutral stimulus is modified so as to become more salient and attention grabbing to the observer, as a result of its association with a desired outcome (e.g., drugs, money). The current study suggests that incentive salience has a particularly powerful influence on the attentional system, overcoming inhibitory control mechanisms that can effectively prevent capture by physically salient stimuli. This may have implications for the development of treatments for substance use disorders that target these attentional biases.
